% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
%\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Ivaylo Toskov}\\
+359894356834\\
ivtoskov@gmail.com
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Work experience}

\begin{itemize}
\item
	\ressubheading{Leanplum}{Sofia, Bulgaria}{Senior Software Engineer}{Senior Software Engineer, October 2017-February 2020}
	\begin{itemize}
	\item Served as the technical lead for Leanplum's A/B testing functionality.
	\item Contributed to the development of a complex reporting engine that handled terabytes of data per day and had a latency SLA of 300ms.
	\item Set up a new team responsible for Email delivery and onboarded 2 engineers.
	\item Conducted 20+ technical and behavioural interviews.
	\item Managed an HDFS cluster with 200+ machines and 2+ petabytes of data.
	\item Worked on the event management of an ingestion engine that handles 27B+ QPS.
	\item Setup and managed an Apache Spark cluster for a machine learning algorithm for sending messages in the optimal time for users.
	\end{itemize}
	Technologies: Java, Python, Google Cloud Platform, Apache Spark, Apache Kafka, HDFS, HBase, Zookeeper, Dataflow, Cloud Pub/Sub, RabbitMQ, BigQuery, GCS, Spring Boot, Git
\item
	\ressubheading{Facebook}{London, UK}{Software Engineer Intern}{Software Engineer Intern, June 2017 - September 2017}
	\begin{itemize}
     \item Implemented an anti-fraud algorithm for video ads delivery based on rate-limiting ad requests.
     \item Built a system for end-to-end testing of video ads.
     \item Rewrote multiple metrics for video view time and impressions based on thorough data analysis.
     \item Introduced various improvements to a system for debugging video related metrics.

	\end{itemize}
Technologies: Hack, Python, Mercurial, Presto, Dataswarm, React, Phabricator
\item
	\ressubheading{Leanplum}{Sofia, Bulgaria}{Software Engineer Intern}{Software Engineer Intern, June 2016-September 2016}
	\begin{itemize}
	\item Rewrote a MapReduce pipeline for sending messages to up to hundreds of millions of users. This resulted in a simplified design and 3x better performance of the module.
     \item Implemented a heuristic for determining the optimal time for sending a message to users with missing data. The algorithm was based on an aggregation of the preferences of all users.
     \item Built a system for monitoring the health of the modules responsible for sending emails and calling webhooks.
     \item Parallelised an algorithm for monitoring the health of task queues, which lead to up to 8x better performance.
	\end{itemize}
Technologies: Java, Python, Google MapReduce, BigQuery, Git
\item
	\ressubheading{Tetracom}{Sofia, Bulgaria}{Software Engineer Intern}{Software Engineer Intern, July 2013-September 2013}
	\begin{itemize}
    \item Built a hybrid mobile application for Android and iOS from scratch
    \item Implemented an API for OAuth 2.0 authentication for a news aggregation project
	\end{itemize}
Technologies: Java, Play Framework, Scala, JavaScript, SVN, Android
\end{itemize}


\resheading{Education}
\begin{itemize}
\item
\ressubheading{ETH Zurich}{}{}{October 2015 - June 2017}
\begin{itemize}
\item Master of Science (MSc), Computer Science, GPA 5.68/6.00, US $\approx$3.70.
\item Thesis: {\it{SIMD intrinsics on managed language runtimes}}. Published at  \href{https://dl.acm.org/doi/10.1145/3168810}{CGO'18}.
\item Received a Master Scholarship for extraordinary academic performance.
\end{itemize}

\item \ressubheading{Vienna University of Technology}{}{}{September 2012 - June 2015}
\begin{itemize}
\item Bachelor of Science (BSc), Computer Science, GPA 1.28, US $\approx$3.90.
\item Worked as a teaching assistant in 2 subjects for 3 semesters.
\end{itemize}

\end{itemize}

\end{document}res